Space Display

### 2021-08-17 graphs_newt_snakes/Space_display.Rmd
this is the slim script i wrote to read in files and an ID to print out the 1st and 1000 generation phenotypes and locations
worked on improving the distribution figures and the files that it needs

```{r space plot, echo=FALSE}
space_data <- read.table("~/Desktop/pulled_info_test.txt", header = TRUE)

ggplot(space_data[which(space_data$gen == 1),], aes(x=loc_x, y=loc_y, color=type)) +
    ggtitle("Start Space: Generation 1", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
    xlab("Longitude") + ylab("Latitude")+
    #theme(plot.title = element_text(size=5)) +
    theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+
    geom_point(aes(alpha=ind_phy))

ggplot(space_data[which(space_data$gen == 1000),], aes(x=loc_x, y=loc_y, color=type)) +
    ggtitle("End Space: Generation 1000", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
    xlab("Longitude") + ylab("Latitude")+
    #theme(plot.title = element_text(size=5)) +
    scale_fill_manual(name = "Species", values = c('TRUE' = "darkred", 'FALSE' = "steelblue"), labels=c("Snakes", "Newts"))+
    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+
    theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
    geom_point(aes(alpha=ind_phy))

@@

ggplot(space_data[which(space_data$gen == 1),], aes(x=ind_phy, color=type, fill=type), alpha=0.3) +
  ggtitle("Start Space: Generation 1", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
  xlab("Phenotype") + ylab("Count")+
  geom_histogram(position="identity", alpha=0.3)+
  geom_vline(data=mu_1gen, aes(xintercept=grp.mean, color=type),
             linetype="dashed")+
  scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+ 
  scale_fill_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+ 
  theme_bw()

ggplot(space_data[which(space_data$gen == 1000),], aes(x=ind_phy, color=type, fill=type), alpha=0.3) +
  ggtitle("Start Space: Generation 1000", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
  xlab("Phenotype") + ylab("Count")+
  geom_histogram(position="identity", alpha=0.3)+
  geom_vline(data=mu_1000gen, aes(xintercept=grp.mean, color=type),
             linetype="dashed")+
  scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+ 
  scale_fill_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Snakes", "Newts"))+ 
  theme_bw()

>>>>

```{r space plot, echo=FALSE}
space_data <- read.table("~/Desktop/Coevo/newt_snake/data/space_test/pulled_info_test.txt", header = TRUE)

space_data$made_max= 0

space_data$made_max<- ifelse(space_data$gen == 1 & space_data$type == "Newt", max(space_data[which(space_data$gen == 1 & space_data$type == "Newt"),]$ind_phy), 
                             ifelse(space_data$gen == 1 & space_data$type == "Snake", max(space_data[which(space_data$gen == 1000 & space_data$type == "Snake"),]$ind_phy),
                                    ifelse(space_data$gen == 1000 & space_data$type == "Newt", max(space_data[which(space_data$gen == 1000 & space_data$type == "Newt"),]$ind_phy), 
                                           ifelse(space_data$gen == 1000 & space_data$type == "Snake", max(space_data[which(space_data$gen == 1000 & space_data$type == "Snake"),]$ind_phy), 0))))

space_data$my_alpha <- space_data$ind_phy/space_data$made_max

ggplot(space_data[which(space_data$gen == 1),], aes(x=loc_x, y=loc_y, color=type)) +
    ggtitle("Start Space: Generation 1", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
    xlab("Longitude") + ylab("Latitude")+
    #theme(plot.title = element_text(size=5)) +
    theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+
    geom_point(aes(alpha=ind_phy))+
    scale_alpha_continuous(name = "Phenotype")

ggplot(space_data[which(space_data$gen == 1000),], aes(x=loc_x, y=loc_y, color=type)) +
    ggtitle("End Space: Generation 1000", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
    xlab("Longitude") + ylab("Latitude")+
    #theme(plot.title = element_text(size=5)) +
    scale_fill_manual(name = "Species", values = c('TRUE' = "darkred", 'FALSE' = "steelblue"), labels=c("Newts", "Snakes"))+
    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+
    theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
    geom_point(aes(alpha=ind_phy))+
    scale_alpha_continuous(name = "Phenotype")

ggplot(space_data[which(space_data$gen == 1),], aes(x=loc_x, y=loc_y, color=type)) +
    ggtitle("Start Space: Generation 1", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
    xlab("Longitude") + ylab("Latitude")+
    #theme(plot.title = element_text(size=5)) +
    theme_bw() +  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+
    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+
    geom_point(aes(alpha=my_alpha))+
    scale_alpha_continuous(name = "Percentage")

ggplot(space_data[which(space_data$gen == 1000),], aes(x=loc_x, y=loc_y, color=type)) +
    ggtitle("End Space: Generation 1000", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
    xlab("Longitude") + ylab("Latitude")+
    geom_point(aes(alpha=my_alpha, color=type)) +
    scale_alpha_continuous(name = "Percentage")+
    #theme(plot.title = element_text(size=5)) +
    scale_fill_manual(name = "Species", values = c('TRUE' = "darkred", 'FALSE' = "steelblue"), labels=c("Newts", "Snakes"))+
    scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+
    theme_bw()  #theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))+

@@

ggplot(space_data[which(space_data$gen == 1),], aes(x=ind_phy, color=type, fill=type), alpha=0.3) +
  ggtitle("Start Space: Generation 1", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
  xlab("Phenotype") + ylab("Count")+
  geom_histogram(position="identity", alpha=0.3)+
  geom_vline(data=mu_1gen, aes(xintercept=grp.mean, color=type),
             linetype="dashed")+
  scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+ 
  scale_fill_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+ 
  theme_bw()

ggplot(space_data[which(space_data$gen == 1000),], aes(x=ind_phy, color=type, fill=type), alpha=0.3) +
  ggtitle("End Space: Generation 1000", subtitle = "file_redo_su_1.11e-11_nu_1.11e-11_sue_0.3_nue_0.3_17018532.txt") +
  xlab("Phenotype") + ylab("Count")+
  geom_histogram(position="identity", alpha=0.3)+
  geom_vline(data=mu_1000gen, aes(xintercept=grp.mean, color=type),
             linetype="dashed")+
  scale_color_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+ 
  scale_fill_manual(name = "Species", values = c('Newt' = "darkred", 'Snake' = "steelblue"), labels=c("Newts", "Snakes"))+ 
  theme_bw()
